Scattering and Pair Processes in General Relativistic Ray Tracing for Neutrinos

### 2016-10-18 paper.tex
Consider dropping the scattering sphere test

\subsection{Homogenous Scattering Star}
[Test presented in~\cite{humm1971-grey_transfer}
and described in~\cite[Sec.~9.1.1]{abdi2012-monte_carlo}.]
\todo{formulate analytic $J$ and $F^\mu$}
\todo{Jerred: setup and run test}

>>>>

\subsection{Homogenous Scattering Star}
\todo{maybe drop this test}
[Test presented in~\cite{humm1971-grey_transfer}
and described in~\cite[Sec.~9.1.1]{abdi2012-monte_carlo}.
Our version would be a point source embedded in a spherical distribution
of purely elastic-scattering material. It requires an analytical estimate
of $J$.]
\todo{formulate analytic $J$.}
